---
title: "Lab7 Twitter API"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Search tweets
```{r message=F}
library(rtweet)
library(ggplot2)
library(maps)
```


Search for up to 1,800 (non-retweeted) tweets containing the rstats hashtag.
```{r}
rt <- search_tweets(
  "#rstats", n = 1800, include_rts = FALSE
)
```

Quickly visualize frequency of tweets over time using `ts_plot()`.

```{r, cache=T}
rt %>%
  ts_plot("3 hours") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #rstats Twitter statuses from past 9 days",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```

Search by geo-location—for example, find 10,000 tweets in the English language sent from the United States. 

```{r, cache=T}
## search for 1,000 tweets sent from the US
rt <- search_tweets(
  "lang:en", geocode = lookup_coords("usa"), n = 1000
)

## create lat/lng variables using all available tweet and profile geo-location data
rt <- lat_lng(rt)

## plot state boundaries
par(mar = c(0, 0, 0, 0))
maps::map("state", lwd = .25)

## plot lat and lng points onto state map
with(rt, points(lng, lat, pch = 20, cex = .75, col = rgb(0, .3, .7, .75)))

```

#Stream tweets

Randomly sample (approximately 1%) from the live stream of all tweets.

```{r, cache=T}
## random sample for 30 seconds (default)
rt <- stream_tweets("")
```


##Get friends

Retrieve a list of all the accounts a user follows.

```{r, cache=T}
## get user IDs of accounts followed by CNN
cnn_fds <- get_friends("cnn")

## lookup data on those accounts
cnn_fds_data <- lookup_users(cnn_fds$user_id)
```

Get followers
Retrieve a list of the accounts following a user.

```{r, cache=T}
## get user IDs of accounts following CNN
cnn_flw <- get_followers("cnn", n = 750)

## lookup data on those accounts
cnn_flw_data <- lookup_users(cnn_flw$user_id)
```

##Get timelines

Get the most recent 1,200 tweets from cnn, BBCWorld, and foxnews.

```{r, cache=T}
## get user IDs of accounts followed by CNN
tmls <- get_timelines(c("cnn", "BBCWorld"), n = 1200)

## plot the frequency of tweets for each user over time
tmls %>%
  dplyr::filter(created_at > "2019-04-29") %>%
  dplyr::group_by(screen_name) %>%
  ts_plot("days", trim = 1L) +
  ggplot2::geom_point() +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    legend.position = "bottom",
    plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of Twitter statuses posted by news organization",
    subtitle = "Twitter status (tweet) counts aggregated by day from May 2019",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```

##Get favorites

Get the 300 most recently favorited statuses by JK Rowling.

```{r, cache=T}
jkr <- get_favorites("jk_rowling", n = 300)
```

##Search users

Search for 100 users with the rstats hashtag in their profile bios.

```{r, cache=T}
## search for users with #rstats in their profiles
usrs <- search_users("#rstats", n = 100)
```

##Get trends

```{r, cache=T}
sf <- get_trends("san francisco")
```


##References
[rtweet](https://rtweet.info/)

